### 2021-04-05 output/report/categorical_imperative_1.tex
updated bibtex for BFP

@@

\isamarkupcmt{This very intuitive theorem holds in my logic but not in Benzmuller Parent's%

@@

Sidebar: the above theorem is really intuitive - it seems like we wouldn't want 
contradictory things to be obligatory in any logic. But for some reason, not only is it not
a theorem of Carmo and Jones' logic, it actually implies some strange conclusions, including 
that everything is either permissible or obligatory. It's not clear to me from a semantic 
perspective why this would be the case. In fact this theorem seems like a desirable 
property. Potential avenue for exploration%
Did some debugging. What was the problem? A misplaced parentheses in the definition 
of ax5b that led to a term being on the wrong side of an implication. Computer Science :(%
After the debugging, all of this is no longer true! On to the next attempt :)%
\isacommand{end}\isamarkupfalse%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/categorical_imperative_1.thy%:%
%:%10=1%:%
%:%11=1%:%
%:%12=2%:%
%:%13=3%:%
%:%27=5%:%
%:%31=7%:%
%:%43=9%:%
%:%47=10%:%
%:%49=12%:%
%:%50=12%:%
%:%51=13%:%
%:%53=14%:%
%:%54=14%:%
%:%56=15%:%
%:%57=15%:%
%:%59=16%:%
%:%60=16%:%
%:%62=17%:%
%:%63=17%:%
%:%64=18%:%
%:%65=19%:%
%:%66=20%:%
%:%67=20%:%
%:%68=21%:%
%:%71=22%:%
%:%75=22%:%
%:%76=22%:%
%:%78=23%:%
%:%79=23%:%
%:%81=24%:%
%:%82=24%:%
%:%84=25%:%
%:%85=25%:%
%:%87=26%:%
%:%88=26%:%
%:%90=27%:%
%:%96=27%:%
%:%99=28%:%
%:%100=29%:%
%:%101=30%:%
%:%102=30%:%
%:%103=31%:%
%:%106=32%:%
%:%110=32%:%
%:%111=32%:%
%:%112=33%:%
%:%114=34%:%
%:%115=34%:%
%:%117=35%:%
%:%118=35%:%
%:%120=36%:%
%:%121=36%:%
%:%123=37%:%
%:%124=37%:%
%:%126=38%:%
%:%132=38%:%
%:%135=39%:%
%:%136=40%:%
%:%137=41%:%
%:%138=41%:%
%:%139=42%:%
%:%142=43%:%
%:%146=43%:%
%:%147=43%:%
%:%149=44%:%
%:%150=44%:%
%:%152=45%:%
%:%158=45%:%
%:%161=46%:%
%:%162=47%:%
%:%163=47%:%
%:%164=48%:%
%:%167=49%:%
%:%171=49%:%
%:%172=49%:%
%:%174=50%:%
%:%175=50%:%
%:%177=51%:%
%:%178=51%:%
%:%180=52%:%
%:%186=52%:%
%:%189=53%:%
%:%190=54%:%
%:%191=54%:%
%:%192=55%:%
%:%195=56%:%
%:%199=56%:%
%:%200=56%:%
%:%202=57%:%
%:%203=57%:%
%:%205=58%:%
%:%206=58%:%
%:%208=59%:%
%:%209=59%:%
%:%211=60%:%
%:%221=63%:%
%:%222=64%:%
%:%223=65%:%
%:%224=66%:%
%:%225=67%:%
%:%226=68%:%
%:%230=70%:%
%:%231=71%:%
%:%235=73%:%
%:%243=75%:%

>>>>

\ \ \isacommand{nitpick}\isamarkupfalse%
{\isacharbrackleft}user{\isacharunderscore}axioms{\isacharbrackright}\isanewline

@@

\isamarkupcmt{This very intuitive theorem holds in my logic but not in BFP's%

@@

\isamarkupcmt{Nitpick found a counterexample for card i = 2:

  Free variable:
    A = ($\lambda x. \_$)($i_1$ := False, $i_2$ := True)%
}%
\endisatagproof
{\isafoldproof}%
%
\isadelimproof
%
\endisadelimproof
%
\begin{isamarkuptext}%
Sidebar: the above theorem is really intuitive - it seems like we wouldn't want 
contradictory things to be obligatory in any logic. But for some reason, not only is it not
a theorem of Carmo and Jones' logic, it actually implies some strange conclusions, including 
that everything is either permissible or obligatory. It's not clear to me from a semantic 
perspective why this would be the case. In fact this theorem seems like a desirable 
property. Potential avenue for exploration%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
Did some debugging. What was the problem? A misplaced parentheses in the definition 
of ax5b that led to a term being on the wrong side of an implication. Computer Science :(%
\end{isamarkuptext}\isamarkuptrue%
%
\begin{isamarkuptext}%
After the debugging, all of this is no longer true! On to the next attempt :)%
\end{isamarkuptext}\isamarkuptrue%
%
\isadelimtheory
%
\endisadelimtheory
%
\isatagtheory
\isacommand{end}\isamarkupfalse%
%
\endisatagtheory
{\isafoldtheory}%
%
\isadelimtheory
%
\endisadelimtheory
%
\end{isabellebody}%
\endinput
%:%file=~/Desktop/cs91r/categorical_imperative_1.thy%:%
%:%10=1%:%
%:%11=1%:%
%:%12=2%:%
%:%13=3%:%
%:%27=5%:%
%:%31=7%:%
%:%43=9%:%
%:%47=10%:%
%:%49=12%:%
%:%50=12%:%
%:%51=13%:%
%:%53=14%:%
%:%54=14%:%
%:%56=15%:%
%:%57=15%:%
%:%59=16%:%
%:%60=16%:%
%:%62=17%:%
%:%63=17%:%
%:%64=18%:%
%:%65=19%:%
%:%66=20%:%
%:%67=20%:%
%:%68=21%:%
%:%71=22%:%
%:%75=22%:%
%:%76=22%:%
%:%78=23%:%
%:%79=23%:%
%:%81=24%:%
%:%82=24%:%
%:%84=25%:%
%:%85=25%:%
%:%87=26%:%
%:%88=26%:%
%:%90=27%:%
%:%96=27%:%
%:%99=28%:%
%:%100=29%:%
%:%101=30%:%
%:%102=30%:%
%:%103=31%:%
%:%106=32%:%
%:%110=32%:%
%:%111=32%:%
%:%112=33%:%
%:%114=34%:%
%:%115=34%:%
%:%117=35%:%
%:%118=35%:%
%:%120=36%:%
%:%121=36%:%
%:%123=37%:%
%:%124=37%:%
%:%126=38%:%
%:%132=38%:%
%:%135=39%:%
%:%136=40%:%
%:%137=41%:%
%:%138=41%:%
%:%139=42%:%
%:%142=43%:%
%:%146=43%:%
%:%147=43%:%
%:%149=44%:%
%:%150=44%:%
%:%152=45%:%
%:%158=45%:%
%:%161=46%:%
%:%162=47%:%
%:%163=47%:%
%:%164=48%:%
%:%167=49%:%
%:%171=49%:%
%:%172=49%:%
%:%174=50%:%
%:%175=50%:%
%:%177=51%:%
%:%178=51%:%
%:%180=52%:%
%:%186=52%:%
%:%189=53%:%
%:%190=54%:%
%:%191=54%:%
%:%192=55%:%
%:%193=56%:%
%:%194=56%:%
%:%197=57%:%
%:%201=57%:%
%:%202=57%:%
%:%204=58%:%
%:%205=58%:%
%:%207=59%:%
%:%208=59%:%
%:%210=60%:%
%:%211=60%:%
%:%213=61%:%
%:%214=61%:%
%:%216=62%:%
%:%217=63%:%
%:%218=64%:%
%:%219=65%:%
%:%229=68%:%
%:%230=69%:%
%:%231=70%:%
%:%232=71%:%
%:%233=72%:%
%:%234=73%:%
%:%238=75%:%
%:%239=76%:%
%:%243=78%:%
%:%251=80%:%
